Use of general purpose graphical processing units with MODFLOW

### 2012-09-17 GW20120518-0099-r01.tex
More box massaging

\hspace{15pt}Each kernel launches a grid of threads composed of one or more blocks of grouped threads. The number of blocks in a grid is determined by the size of the kernel data being processed or the number of SM. The total number of threads in a grid is equal to the number of threads per block times the number of blocks. CCs on each SM can run one or more blocks but blocks are restricted to a single CC. Threads within a block are further grouped into warps, which is the maximum number of threads that are managed and processed simultaneously in each block. Multiple warps execute one after another to complete block processing of the kernel. GPGPU architecture and kernel execution are shown graphically in \textbf{figure~\ref{FigParallel}}.

\hspace{15pt}The Tesla C2050 used in this study has the following specifications: SMs = 14, CC per SM = 32, threads per block = 1,024, and warp size = 32. The multi-threaded instruction unit on each of the 14 Tesla C2050 SMs can run 48 warps concurrently, yielding a total of 21,504 concurrent threads (14 SMs $\times$ 48 warps per SM $\times$ 32 threads per warp).\\ \color{black}
}}

>>>>

\hspace{15pt}Each kernel launches a CUDA grid, which is composed of one or more blocks of grouped threads. Threads within the same block can share certain types of physical memory on the GPGPU.  The number of blocks in a grid is determined by the size of the kernel data being processed or the number of SM. The total number of threads in a grid is equal to the number of threads per block times the number of blocks. CCs on each SM can run one or more blocks but blocks are allocated to a single CC. Threads within a block are further subdivided into warps for processing; a warp is the maximum number of threads that are managed and processed simultaneously within each block. Multiple warps execute one after another to complete block processing of the kernel. GPGPU architecture and kernel execution are shown graphically in \textbf{figure~\ref{FigParallel}}.

\hspace{15pt}The Tesla C2050 used in this study has the following specifications: SMs = 14, CC per SM = 32, threads per block = 1,024, and threads per warp = 32. The multi-threaded instruction unit on each of the 14 Tesla C2050 SMs can run 48 warps concurrently, yielding a total of 21,504 concurrent threads (14 SMs $\times$ 48 warps per SM $\times$ 32 threads per warp).\\ \color{black}
}}
